---
title: SJP Data Catalog Resources Report
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: html_document
params:
  saved_res_df: NULL
  type_hist: NULL
  year_hist: NULL
  tags_hist: NULL
  tags_connect: NULL
always_allow_html: TRUE
---

```{r, echo=FALSE, warning=FALSE}
library(gt)
library(plotly)
library(htmltools)
# library(wordcloud)
# library(d3wordcloud)
library(sankeyD3)
```

# Saved Resources

```{r, echo=FALSE}
saved_res <- params$saved_res_df
rownames(saved_res) <- NULL
# saved_res$Link <- paste0("[", params$saved_res_df$Link, "](", params$saved_res_df$Link, ")")
# knitr::kable(saved_res, caption = "Set of Saved Resources")

make_hyperlink = function(url, text=url) {
  paste('<a href="', url, '">', text, '</a>')
}

saved_res %>%
gt() %>%
  fmt (
    columns = 'Link',
    fns = make_hyperlink
  ) %>%
  cols_width(
    "Name" ~ px(40),
    "Source" ~ pct(30),
    "Link" ~ pct(30)
  )
```


# Meta-Analysis

This report includes visualizations which explore the contents of your Saved Resources from an overarching conceptual lens. The following plots and visuals will help visualize the types of features and themes present among the specified set of resources. Though the specific interpretations of these figures will vary depending on the set of resources you are considering, each section below includes a brief explanation of its contents and how the resulting figures might be interpreted.

## Types of Resources

The following distribution will help you visualize what the spread of resource types present among the set of saved resources. 

```{r, echo=FALSE, fig.show="hold", out.width="100%"}
data <- data.frame(params$type_hist, stringsAsFactors = FALSE)
    
# Organize the values by counts from greatest to least
if (nrow(data) > 1) {
  data$all_types <- factor(data$all_types, levels = unique(data$all_types)[order(data$Freq, decreasing = TRUE)])
  x_vals <- data$all_types
  y_vals <- data$Freq
} else {
  # No need to sort if there's only one type of count
  x_vals <- names(params$type_hist)
  y_vals <- as.numeric(params$type_hist)
}

type_fig <- plot_ly(
  x = x_vals,
  y = y_vals,
  type = "bar",
)
type_fig <- type_fig %>% layout(title = "Resource Types", yaxis = list(title = "Count"))
type_fig
```

## Years Available

The following distribution will help you visualize what years of data are available among the set of saved resources. This plot may reveal that the available data is more concentrated during a certain time period or may be uniformly spread out across time.

```{r, echo=FALSE, fig.show="hold", out.width="100%"}
year_fig <- plot_ly(
      x = names(params$year_hist),
      y = as.numeric(params$year_hist),
      type = "bar"
)
year_fig <- year_fig %>% layout(title = "Years Available", yaxis = list(title = "Count"))
year_fig
```

## Tags

The tags distribution shows the frequency of each tag that occurs within the set of Saved Resources. This plot helps highlight the general breadth or scope of domains and features present in the resource set as well as which of those features are most prominent. 

```{r, echo=FALSE, fig.show="hold", out.width="100%"}
data <- data.frame(params$tags_hist, stringsAsFactors = FALSE)
colnames(data) <- c("word", "freq")
# No need to sort if there's only one type of tag
if (nrow(data) > 1) {
  # Organize the values by counts from greatest to least
  data$word <- factor(data$word, levels = unique(data$word)[order(data$freq, decreasing = FALSE)])
}

tags_fig <- plot_ly(
  x = data$freq,
  y = data$word,
  type = "bar",
  # mode = "markers"
)
tags_fig <- tags_fig %>% layout(
  title = "Tags Distribution",
  yaxis = list(tickfont = list(size = 10)),
  xaxis = list(title = "Count"),
  shapes = lines)

# tags_wordcloud <- wordcloud(words=data$Var1, freq=data$Freq, min.freq = 1, max.words=200, random.order=FALSE, rot.per=0.35, colors=brewer.pal(8, "Dark2"))

# tags_wordcloud <- wordcloud2(data=data, minRotation=0, maxRotation=0, color="random-dark")

# tags_wordcloud <- d3wordcloud(
#   words = data$Var1, 
#   freq = data$Freq, 
#   rotate.min = 0,           
#   rotate.max = 0,
#   tooltip = TRUE,
#   font = "Arial",
#   spiral = "rectangular"
# )

tags_fig
# tags_wordcloud
```

## Domain Connections

The following network diagram shows the different flows or connections between various resource attributes. This is useful for investigating how certain features and domains are related to each other; that is, what types of domains are nested within the broader resource types and what types of features are available within those domains. For example, examining the flows from the "Health" node to the various stratification nodes might reveal that there are already many resources within the health domain that are race/ethnicity and gender stratified but there are none that are disability stratified. This type of analysis has the potential to not only highlight what features of the data are represented, but also reveal where there might be existing gaps among the available resources, providing opportunities for novel contributions.

```{r, include=FALSE}
nodes <- params$tags_connect$nodes
color_map <- unique(nodes[c("group", "color", "x_pos")])
level_map <- list("0"="Resource Type", "1"="Data Subject", "2"="Data Attribute")
current_level <- -1

legend <- ""

for (i in 1:nrow(color_map)) {
  label <- color_map[i, "group"]
  color <- color_map[i, "color"]
  level <- color_map[i, "x_pos"]
  
  if (level != current_level) {
    legend <- paste0(legend, "<br><span><b>", level_map[[toString(level)]], ":&nbsp;</b></span>")
    current_level <- current_level + 1
  }
  
  legend <- paste0(legend, '<span style="background-color:', color, '; border:1px solid black; height:11px; width:11px; display:inline-block"></span><span>&nbsp;', label, '&emsp;<span>')
}

file_create <- file.create("tmp/sankey_legend.html")
writeLines(legend, "tmp/sankey_legend.html")
```
```{r, echo=FALSE}
includeHTML("tmp/sankey_legend.html")
```
```{r, include=FALSE}
file_remove <- file.remove("tmp/sankey_legend.html")
```

```{r, echo=FALSE, fig.show="hold", out.width="100%"}
sankeyNetwork(
  Links = params$tags_connect$links,
  Nodes = params$tags_connect$nodes,
  Source = "IDsource",
  Target = "IDtarget",
  Value = "value",
  NodeID = "name",
  NodeGroup = "group",
  NodeColor = "color",
  NodePosX = "x_pos",
  iterations = 0,
  zoom = TRUE,
  dragX = FALSE,
  dragY = FALSE,
  showNodeValues = FALSE,
  highlightChildLinks = TRUE,
  numberFormat = ".0f",
  linkOpacity = 0.25
)
```